---
title: "RWorksheet_Porras4"
author: "Porras, Dorlyne Fate"
date: "2022-11-23"
output: pdf_document
---

1. The table below shows the data about shoe size and height. Create a data frame.

```{r, error = TRUE}
Shoesize <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,
              13.0,7.5,10.5,8.5,12.0,10.5,
              13.0,11.5,8.5,5.0,10.0,
              6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)
Height <- c(66.0,68.0,64.5,65.0,70.0,
            64.0,70.0,71.0,72.0,64.0,
            74.5,67.0,71.0,71.0,77.0,72.0,
            59.0,62.0,72.0,66.0,64.0,67.0,73.0,
            69.0,72.0,70.0,69.0,70)
Gender <- c("F","F","F","F","M","F","M","F","M",
            "M","M","F","M","M","M","M","F","F",
            "M","F","M","M","M","F","M","M","M","M")

data_frame <- data.frame(Shoesize,Height,Gender)
data_frame

```

b. Find the mean of shoe size and height of the respondents. Copy the codes and results.

```{r, error = TRUE}
summary(data_frame)
```

SHOESIZE: Mean   : 9.411
HEIGHT:   Mean   :68.57 

c. Is there a relationship between shoe size and height? Why?

 Yes, The Higher the height, the greater the shoesize.


2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.

Consider data consisting of the names of months:

  "March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February","April")

```{r, error = TRUE}
Months <- c("March","April","January","November","January",
            "September","October","September","November","August",
            "January","November","November","February","May","August",
            "July","December","August","August","September","November","February","April")

factor_Months <- factor(Months)
factor_Months

```

3. Then check the summary() of the months_vector and factor_months_vector. |
  Interpret the results of both vectors. Are they both equally useful in this case?

```{r, error = TRUE}
summary(Months)
```

```{r, error = TRUE}
summary(factor_Months)
```

4. Create a vector and factor for the table below.

```{r, error = TRUE}
factor_data <- c(1,4,3)
```

```{r, error = TRUE}
new_order_data <- factor(factor_data,levels = c("East","West","North"))
```

```{r, error = TRUE}
print(new_order_data)
```

5. Enter the data below in Excel with file name = import_march.csv
a. Import the excel file into the Environment Pane using read.table() function.
Write the code.

```{r, error = TRUE}
dataTable <- read.table("/cloud/project/import_march.csv", header=TRUE, sep = ",")
dataTable
```

b. View the dataset. Write the code and its result.

```{r, error = TRUE}
dataTable <- read.csv("/cloud/project/import_march.csv")
dataTable
```

